Dusty Days and a Vibrio Craze: The Influence of Saharan Dust Deposition on Microbial Communities in High Nutrient Coastal Waters 

### 2023-05-02 code/analysis_code/stats/5_multi_variate_models/random_forest_models.qmd
Made direct path to images in mansscript

rf_residual_plot <- ggplot(rf_residuals, 
                              aes(y = .resid, 
                                  x = .pred)) + 
  geom_point() + 
  labs(title = "Blind Oso: Predictions vs Residuals: Random Forest", 
       x = "Copies/mL Prediction", 
       y = "Residuals")
plot(rf_residual_plot) + #view plot
  theme_bw()
```

@@

@@

>>>>

ggsave(here("results", "plots", "rf_bo.png"))
```

```{r}
rf_residual_plot <- ggplot(rf_residuals, 
                              aes(y = .resid, 
                                  x = .pred)) + 
  geom_point() + 
  labs(title = "Blind Oso: Predictions vs Residuals: Random Forest", 
       x = "Copies/mL Prediction", 
       y = "Residuals")
plot(rf_residual_plot) + #view plot
  theme_bw()
```

@@

ggsave(here("results", "plots", "rf_c2.png"))

```{r}
rf_residual_plot <- ggplot(rf_residuals, 
                              aes(y = .resid, 
                                  x = .pred)) + 
  geom_point() + 
  labs(title = "Predictions vs Residuals: Random Forest", 
       x = "Copies/mL Prediction", 
       y = "Residuals")
plot(rf_residual_plot) #view plot
```

@@

ggsave(here("results", "plots", "rf_rd.png"))

```{r}

### 2023-05-02 products/manuscript/Manuscript.qmd
Made direct path to images in mansscript

![Figure 1: Dust Aerosol Optical Density (AOD) over daily time series.](images/000009-01.png)

@@

![Figure 2: Vibrio gene copies/mL over daily time series across site.](images/000005-03.png)

@@

![Figure 3: Envonmental parameters across daily time series with color by site.](images/000019.png)

@@

![Figure 5: Linear Regression Output for Dust AOD (log-transformed) and Vibrio gene copies/mL](images/000055.png){width="1491"}

@@

![Figure 6: Vibrio gene copies/mL at Blind Oso predicted by Random Forest](images/000017-02.png)

![Figure 7: Vibrio gene copies/mL at Canals predicted by Random Forest](images/000007-02.png)

![Figure 8: Vibrio gene copies/mL at the Gulf predicted by Random Forest](images/000007-03.png)

>>>>

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 1: Dust Aerosol Optical Density (AOD) over daily time series"}
knitr::include_graphics(here("results", "plots", "dust.png"))
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 2: Vibrio gene copies/mL over daily time series across site"}
knitr::include_graphics(here("results", "plots", "copies.png"))
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 3: Envonmental parameters across daily time series with color by site"}
knitr::include_graphics(here("results", "plots", "env.png"))
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 5: Linear Regression Output for Dust AOD (log-transformed) and Vibrio gene copies/mL"}
knitr::include_graphics(here("results", "plots", "uni.png"))
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 6: Vibrio gene copies/mL at Blind Oso predicted by Random Forest"}
knitr::include_graphics(here("results", "plots", "rf_bo.png"))
```

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 7: Vibrio gene copies/mL at Canals predicted by Random Forest"}
knitr::include_graphics(here("results", "plots", "rf_c2.png"))
```

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 8: Vibrio gene copies/mL at the Gulf predicted by Random Forest"}
knitr::include_graphics(here("results", "plots", "rf_rd.png"))
```
